Exploring the Usefulness of Varactor loaded Nonlinear Transmission Lines

### 2020-06-03 RohdeAndSchwarzWhitePaper/Draft_White_Paper.tex
Added AC Response Section and filled in more detail for each section

%% bare_jrnl.tex
%% V1.4a
%% 2014/09/17
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8a or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_conf_compsoc.tex,
%%                    bare_jrnl_compsoc.tex, bare_jrnl_transmag.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices and paper sizes can       ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

@@

%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\usepackage{cite}

% *** GRAPHICS RELATED PACKAGES ***
%
%\ifCLASSINFOpdf
  \usepackage{graphicx}
  % declare the path(s) where your graphic files are
\graphicspath{{./images/}{./images/Board1/}{./images/Board2/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % declare the path(s) where your graphic files are
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
%  \DeclareGraphicsExtensions{.bmp}
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

@@

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% % % than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
%
\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
\usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Exploring the Usefulness of Varactor loaded Nonlinear Transmission Lines}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2014 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
 In this paper we will discuss the use of nonlinear elements within
a transmission line to study their effects on the speed and shape of
an input pulse, and how the next group which takes over our work may use this information to design similar circuits with improved bandwidth and/or performance.
\end{abstract}

@@

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart  {T}he goal of this project was to explore how non-linear transmission lines behave when loaded with varactors and how they can be used. Using design methodologies taken from previous studies and IEEE research, we have constructed a varactor loaded transmission line and attempted to observe and replicate the pulse sharpening effect shown in the literature.

@@

While nonlinear capacitors have been used in many studies \cite{FastHighVoltageNLTL} when implementing this design in high power systems, varactor diodes have the advantage of a larger capacitance range, and allow us to perform measurements using lower voltages. In addition, the overall design is simplified with the use of Varactors because only one bias is needed.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth,page={1}]{Probed_Input_N10_N240_NoSeriesResistance.pdf}
\caption{\ Comparing Risetime in Simulations at Input node Node 10 and Node 240
}\label{fig:ProbedTransientNoSer}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth,page={1}]{Probed_Input_N10_N240_With_SeriesResistance.pdf}
\caption{\
}\label{fig:ProbedTransientYesSer}
\end{figure}

@@

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{ACResponseB1}
\caption{Simulated AC Response for Board 1}
\label{fig:simACBoard1}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{MeasuredACResponseB2.png}
\caption{Measured Frequency Response for Board 2 (L= 560nH)}
\label{fig:MeasACBoard2}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{ACResponseB1}
\caption{Simulated AC Response for Board L=560nH}
\label{fig:simACBoard2}
\end{figure}

@@

>>>>

% % bare_jrnl.tex % V1.4a % 2014/09/17 % by Michael Shell % see
% http://www.michaelshell.org/ % for current contact information.
% % % This is a skeleton file demonstrating the use of IEEEtran.cls % (requires
% IEEEtran.cls version 1.8a or later) with an IEEE % journal paper.
% % % Support sites:
% % http://www.michaelshell.org/tex/ieeetran/ %
% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/ % and %
% http://www.ieee.org/

% %************************************************************************* %
% Legal Notice:
% % This code is offered as-is without any warranty either expressed or %
% implied; without even the implied warranty of MERCHANTABILITY or % FITNESS FOR
% A PARTICULAR PURPOSE! % User assumes all risk.
% % In no event shall IEEE or any contributor to this code be liable for % any
% damages or losses, including, but not limited to, incidental, % consequential,
% or any other damages, resulting from the use or misuse % of any information
% contained here.
% % % All comments are the opinions of their respective authors and are not %
% necessarily endorsed by the IEEE.
% % % This work is distributed under the LaTeX Project Public License (LPPL) % (
% http://www.latex-project.org/ ) version 1.3, and may be freely used, %
% distributed and modified. A copy of the LPPL, version 1.3, is included % in
% the base LaTeX documentation of all distributions of LaTeX released %
% 2003/12/01 or later.
% % Retain all contribution notices and credits.
% % ** Modified files should be clearly indicated as such, including  ** % **
% renaming them and changing author support contact information. ** % % File
% list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex, % bare_conf.tex,
% bare_jrnl.tex, bare_conf_compsoc.tex, % bare_jrnl_compsoc.tex,
% bare_jrnl_transmag.tex
% %*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices and paper sizes can       ***
% *** trigger bugs that do not appear when using other class files.       ***
% *** The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

@@

% If IEEEtran.cls has not been installed into the LaTeX system files, manually
% specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

% *** MISC UTILITY PACKAGES ***  \usepackage{ifpdf} Heiko Oberdiek's ifpdf.sty
% is very useful if you need conditional compilation based on whether the output
% is pdf or dvi.
% usage:
% \ifpdf % pdf code \else % dvi code \fi The latest version of ifpdf.sty can be
% obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/ Also, note that
% IEEEtran.cls V1.7 and later provides a builtin \ifCLASSINFOpdf conditional
% that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may have to
% be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
\usepackage{cite}

% *** GRAPHICS RELATED PACKAGES ***  \ifCLASSINFOpdf
  \usepackage{graphicx}
  % declare the path(s) where your graphic files are
\graphicspath{{./images/}{./images/Board1/}{./images/Board2/}}
  % and their extensions so you won't have to specify these with every instance
  % of \includegraphics or other class option (dvipsone, dvipdf, if not using
  % dvips). graphicx will default to the driver specified in the system
  % graphics.cfg if no driver is specified.
  % declare the path(s) where your graphic files are and their extensions so you
  % won't have to specify these with every instance of \includegraphics
% \DeclareGraphicsExtensions{.bmp} graphicx was written by David Carlisle and
% Sebastian Rahtz. It is required if you want graphics, photos, etc.
% graphicx.sty is already installed on most LaTeX systems. The latest version
% and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/ Another good
% source of documentation is "Using Imported Graphics in LaTeX2e" by Keith
% Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/  latex, and pdflatex in dvi
% mode, support graphics in encapsulated postscript (.eps) format. pdflatex in
% pdf mode supports graphics in .pdf, .jpeg, .png and .mps (metapost) formats.
% Users should ensure that all non-photo figures use a vector format (.eps,
% .pdf, .mps) and not a bitmapped formats (.jpeg, .png). IEEE frowns on
% bitmapped formats which can result in "jaggedy"/blurry rendering of lines and
% letters as well as large increases in file sizes.
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides many
% useful and powerful commands for dealing with mathematics. If using it, be
% sure to load this package with the cmex10 option to ensure that only type 1
% fonts will utilized at all point sizes. Without this option, it is possible
% that some math symbols, particularly those within footnotes, will be rendered
% in bitmap form which will result in a document that can not be IEEE Xplore
% compliant!  Also, note that the amsmath package sets \interdisplaylinepenalty
% to 10000 thus preventing page breaks from occurring within multiline
% equations. Use:
\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***  \usepackage{algorithmic} algorithmic.sty
% was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure environment
% to provide for a floating algorithm. Do NOT use the algorithm floating
% environment provided by algorithm.sty (by the same authors) or algorithm2e.sty
% (by Christophe Fiorio) as IEEE does not use dedicated algorithm float types
% and packages that provide these will not provide correct IEEE style captions.
% The latest version and documentation of algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/ There is also
% a support site at:
% http://algorithms.berlios.de/index.html Also of interest may be the
% (relatively newer and more customizable) algorithmicx.sty package by Szasz
% Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves the
% standard LaTeX2e array and tabular environments to provide better appearance
% and additional user controls. As the default LaTeX2e table generation code is
% lacking to the point of almost being broken with respect to the quality of the
% end results, all users are strongly advised to use an enhanced (at the very
% least that provided by array.sty) set of table tools. array.sty is already
% installed on most systems. The latest version and documentation can be
% obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

@@

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement for
% subfigure.sty, the latter of which is no longer maintained and is incompatible
% with some LaTeX packages including fixltx2e. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls' handling of captions and this will result in non-IEEE style
% figure/table captions. To prevent this problem, be sure and invoke
% subfig.sty's "caption=false" package option (available since subfig.sty
% version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls handling of
% captions.
% Note that the Computer Society format requires a larger sans serif font % %
% than the serif footnote size font used in traditional IEEE formatting and thus
% the need to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by Frank
% Mittelbach and David Carlisle. This package corrects a few problems in the
% LaTeX2e kernel, the most notable of which is that in current LaTeX2e releases,
% the ordering of single and double column floats is not guaranteed to be
% preserved. Thus, an unpatched LaTeX2e can allow a single column figure to be
% placed prior to an earlier double column figure. The latest version and
% documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

% \usepackage{stfloats} stfloats.sty was written by Sigitas Tolusis. This
% package gives LaTeX2e the ability to do double column floats at the bottom of
% the page as well as the top. (e.g., "\begin{figure*}[!b]" is not normally
% possible in LaTeX2e). It also provides a command:
% \fnbelowfloat to enable the placement of footnotes below bottom floats (the
% standard LaTeX2e kernel puts them above bottom floats). This is an invasive
% package which rewrites many portions of the LaTeX2e float routines. It may not
% work with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/ Do not use the
% stfloats baselinefloat ability as IEEE does not allow \baselineskip to
% stretch. Authors submitting work to the IEEE should note that IEEE rarely uses
% double column equations and that authors should try to avoid such use. Do not
% be tempted to use the cuted.sty or midfloat.sty packages (also by Sigitas
% Tolusis) as IEEE does not format its papers in such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features of both
% fixltx2e and stfloats:
\usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

% \ifCLASSOPTIONcaptionsoff \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}} \fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and Axel
% Sommerfeldt. This package may be useful when used in conjunction with
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at the
% end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line spacing
% as well. Be sure and use the nomarkers option of endfloat to prevent endfloat
% from "marking" where the figures would have been placed in the text. The two
% hack lines of code above are a slight modification of that suggested by in the
% endfloat docs (section 8.4.1) to ensure that the full captions always appear
% in the list of figures/tables - even if the user used the short optional
% argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument, so
% this should not be an issue. A similar trick can be used to disable captions
% of packages such as subfig.sty that lack options to turn off the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}} However, the above
% trick will not work if both optional arguments of the \subfloat command are
% used. Furthermore, there needs to be a description of each subfigure
% *somewhere* and endfloat does not add subfigure captions to its list of
% figures. Thus, the best approach is to avoid the use of subfigure captions
% (many IEEE journals avoid them anyway) and instead reference/explain all the
% subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/  The IEEEtran
% \ifCLASSOPTIONcaptionsoff conditional can also be used later in the document,
% say, to conditionally put the References on a page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/ Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. *** *** Do
% not use packages that alter fonts (such as pslatex).         *** There should
% be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan to
% submit to, of course. )

@@

\begin{document}
% paper title Titles are generally capitalized except for words such as a, an,
% and, as, at, but, by, for, in, nor, of, on, or, the, to and up, which are
% usually not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Exploring the Usefulness of Varactor loaded Nonlinear Transmission Lines}
% author names and IEEE memberships note positions of commas and nonbreaking
% spaces ( ~ ) LaTeX will not break a structure at a ~ so this keeps an author's
% name from being broken across two lines.
% use \thanks{} to gain access to the first footnote area a separate \thanks
% must be used for each paragraph as LaTeX2e's \thanks was not built to handle
% multiple paragraphs

@@

% note the % following the last \IEEEmembership and also \thanks - these prevent
% an unwanted space from occurring between the last author name and the end of
% the author line. i.e., if you had this:
% \author{....lastname \thanks{...} \thanks{...} }
% ^------------^------------^----Do not want these spaces!  a space would be
% appended to the last name and could cause every name on that line to be
% shifted left slightly. This is one of those "LaTeX things". For instance,
% "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get "AB" then you
% have to do: "\textbf{A}\textbf{B}" \thanks is no different in this regard, so
% shield the last } of each \thanks that ends a line with a % and do not let a
% space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth, this
% is a minor point as most people would not even notice if the said evil space
% somehow managed to creep in.

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% *** Note that you probably will NOT want to include the author's *** *** name
% in the headers of peer review papers.                   *** You can use
% \ifCLASSOPTIONpeerreview for conditional compilation here if you desire.

% If you want to put a publisher's ID mark on the page you can do it like this:
% \IEEEpubid{0000--0000/00\$00.00~\copyright~2014 IEEE} Remember, if you use
% this you must call \IEEEpubidadjcol in the second column for its text to clear
% the IEEEpubid mark.

% use for special paper notices \IEEEspecialpapernotice{(Invited Paper)}

@@

% As a general rule, do not put math, special symbols or citations in the
% abstract or keywords.
\begin{abstract}
 In this paper we will discuss the use of nonlinear elements within
a transmission line to study their effects on the speed and shape of
an input pulse, and how the next group which takes over our work may use this
information to design similar circuits with improved bandwidth and/or
performance.
\end{abstract}

@@

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN DOCUMENT BEGINS HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\IEEEPARstart  {T}he goal of this project was to explore how non-linear
transmission lines behave when loaded with varactors and how they can be used.
Using design methodologies taken from previous studies and IEEE research, we
have constructed a varactor loaded transmission line and attempted to observe
and replicate the pulse sharpening effect shown in the literature.

@@

While nonlinear capacitors have been used in many studies

\cite{FastHighVoltageNLTL} when implementing this design in high power systems,
varactor diodes have the advantage of a larger capacitance range, and allow us
to perform measurements using lower voltages. In addition, the overall design is
simplified with the use of Varactors because only one bias is needed.

@@

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.35\textwidth,angle = -90]{ACResponseB1}
\caption{Simulated AC Response for Board 1}
\label{fig:simACBoard1}
\end{figure}

@@

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{MeasuredSpectrum.png}
\caption{}
\label{fig:MeasSpec}
\end{figure}
